The behaviour of fundamental particles and forces are described by the Standard Model (SM) of
particle physics.
For a long time validation of the SM relied upon the discovery of a scalar Higgs boson, which was
observed in 2012~\cite{Chatrchyan:2012ufa,Aad:2012tfa} by the
\cms~\cite{Chatrchyan:2012ufa} and \atlas~\cite{Aad:2012tfa} collaborations.
This final piece of the picture has made the SM a remarkably robust theory with no predictions
deviating significantly from experimental observations.
Indeed, the fine structure constant, $\alpha$, which characterizes the coupling strength of
electromagnetic interactions
% is one of the most accurately predicted physical values.  The value of $\alpha^{-1}$
is measured to be:
\begin{equation}
  \alpha^{-1} = 137.035 999 074 (44),
\end{equation}
with a relative uncertainty of 0.32 parts per billion~\cite{PDG2012}.
While the current best theoretical prediction, which accounts for up to tenth order Feynman
diagrams, is:
\begin{equation}
  \alpha^{-1} = 137.035 999 073 (35),
\end{equation}
to an accuracy of 0.25 parts per billion~\cite{Aoyama:2012wj}.
Agreement between such precisely measured values, makes the theory of Quantum Electrodynamics, which
describes interactions of photons and charged particles in the SM, one of the most accurate
theories yet constructed.

%Motivation for CP and flavour violation goes here...

%%Despite countless measurements being in agreement with SM theoretical predictions, it is well known
Despite its countless successes,
there are many arguments suggesting that the SM is an incomplete
picture of particle physics.
%%Experimental observations that are it is well known that the SM is incomplete; arguments for this
%%come from both the experimental and theoretical
%%leaves some experimentally observed phenomena unexplained.
%Experimentally, there are observed phenomena which are left unexplained by the SM.
%Neutrinos are treated as massless in the SM, but they are seen to oscillate in flavour space
%indicating that they must, in fact, have mass.
%Flat rotation curves of galaxies and gravitational lensing indicate the existence of Dark Matter,
%which is entriely unaccounted for by the SM.
%%Shortcomings include the
%% credence
%%For example the SM does not explain: gravity, dark matter, dark energy, and neutrino masses.
One problem is that the SM cannot reconcile the matter-antimatter asymmetry observable in the
Universe today.
The hypothesized process which caused this asymmetry is known as baryogenesis.
%Baryogenesis is the term for a hypothesized process which resulted in the matter-dominated nature of
%the Universe.
%Whatever this process may be, it must include:
%\begin{itemize}
  %\item at least one baryon number (B) violating process,
  %\item Charge and Charge-Parity (CP) violation,
  %\item interactions out of thermal equilibrium.
%\end{itemize}
Whatever this process may be it must satisfy the three Sakharov
conditions~\cite{1991SvPhU..34..392S}; which outline minimum requirements for baryogenesis.
The first, most obvious, criteria is that baryogenesis must violate baryon number, $B$; because at
the time the Big Bang, $B=0$, whereas today $B\gg0$.
%These are the Sakharov conditions~\cite{1991SvPhU..34..392S}, and outline the minimum requirements
%of baryogenesis.
%The first of these criteria is an obvious one: at the time of the Big Bang $B=0$, whereas today
%$B\gg0$; hence $B$ must not be conserved in some process.
The second Sakharov condition is that both Charge (C) and Charge-Parity (CP) are violated.
If C were conserved, then for a particle $X$ decaying into a particle $Y$ and $q$, where $q$ is
baryonic:
\begin{equation}
  \Gamma\big(X\to Y+q\big)=\Gamma\big(\Xbar{X} \to \Xbar{Y}+\bar q\big),
\end{equation}
which would lead to $B$ being conserved over time.
Violation of C alone is insufficient.
Consider a process $X\to q_Lq_L$ which has a CP-conjugate process $\bar X\to \bar q_R\bar q_R$;
then
\begin{equation}
  \Gamma\big(X\to q_Lq_L\big) + \Gamma\big(X\to q_Rq_R)
  =
  \Gamma\big(\Xbar{X}\to \bar q_R\bar q_R\big) + \Gamma\big(\Xbar{X}\to \bar q_L\bar q_L\big)
\end{equation}
would still result in $B$ conservation even if C is violated.
Thus, the process must be CP violating.
The final criteria ensures that baryogenesis occurs at a higher rate than anti-baryogenesis.
%Clearly the process must result in the violation of baryon number, and it must happen out of
%thermal equilibrium otherwise the process would occur equally as often in each direction.
%The third condition, CP violation (CPV) means that
%$\Gamma(A+B\to C)\neq\Gamma(\bar A + \bar B \to \bar C)$, so the annihilation of the products of
%the interaction cannot washout the asymmetry.
%The flavour sector contains the only source of CPV in the SM, but comes up short by around 10
%orders of magnitude when explaining the matter dominated nature of the
%Universe~\cite{Cline:2006ts,Huet:1994jb}.
%There is therefore a powerful reason to believe that NP might enter the flavour sector.
%The only source of CPV in the SM is found in the flavour sector,

The following chapter will elucidate as to how the flavour sector is the only source of CPV in the
SM.
It will then go on to motivate study of flavour physics at \lhcb by exploring some problems with
the SM as a theory.

%The flavour sector also contains the only source of flavour violation in the SM.
%The flavour sector provides an ideal environment for indirect searches of new physics,





