\section{Operator Product Expansion}

%The most pessimistic solution to the flavour problem is Minimal Flavour Violation (MFV)
%which simply assumes that beyond SM physics follows a Yukawa coupling like structure in the flavour
%sector, this would lead to no discernible new physics in the flavour sector.


When describing macroscopic physical systems, it is frequently necessary to simplify the situation by making
assumptions about the distance scales involved.
One would not, for example, dream of using quantum mechanics to model a ball colliding with a wall
despite the fact that the treatment would be far more proper than a Newtonian approach.
An \EFT does the same thing in particle physics
by decoupling the short- and long-range interactions, and treating them separately.
Contributions from particles with very high mass, much greater than $\mu$ are suppressed.
%An equally valid interpretation is that massive, unstable particles have short lifetimes and can
%only interact over very small distances.
These simplifications are greatly advantageous, allowing processes to be modelled at a scale
relevant to the particles involved.
A canonical example of this is Fermi's effective theory of weak decays which predates electroweak
theory; in it, a process (such as $\beta$-decay) is collapsed into a four point interaction.

Creating an effective field theory for particle physics begins by defining an energy scale,
$\Lambda$, which separates the long and short range interactions.
For the case of a process involving a decaying \bquark quark, with initial state $\ket{i}$ and
final state $\ket{f}$,
the energies are of order $m_\bquark$.
In the full treatment of the SM, contributions from the \tquark quark and weak bosons --- which all
have masses $\mathcal{O}(100\gev)$ --- must be accounted for.
Therefore, an appropriate choice for $\Lambda$ is $\sim m_W$.
Heavy fields above $\Lambda$ are then integrated out and are parameterized by complex numbers,
known as Wilson coefficients, $C$.
The remaining physics is encapsulated in the long distances operators, $\mathcal{O}$, each having
its own gauge group defining a particular type of process.
Transition matrix elements for the interaction in the effective Hamiltonian are
\begin{equation}
  \bra{f}\Ham{eff}\ket{i} =
  \sum_j C_j(\Lambda)\bra{f}\Op{j}^{(d)}\ket{i}\Big|_{\Lambda}.
  \label{eq:th:opeham}
\end{equation}
Which is simply a weighted sum over the long distance matrix elements $\bra{f}\Op{j}\ket{i}$.

The above sum runs over an infinite number of operators --- which is clearly impractical.
To simplify matters one can extract factors of $\Lambda^{-1}$ from the Wilson coefficients
making the coefficients dimensionless.
This modifies the effective Hamiltonian to be a sum over dimensions, $d$:
\begin{equation}
  \bra{f}\Ham{eff}\ket{i} =
  \sum_{d}\frac{1}{\Lambda^{d}}
  \sum_j c_j^{(d)}\bra{f}\Op{j}^{(d)}\ket{i}\Big|_{\Lambda}.
  \label{eq:th:opehamnorm}
\end{equation}
This is entirely general, and one can calculate the Wilson coefficients to a high degree of
accuracy --- using perturbative methods --- in the SM and many BSM extensions.
Calculating the long distance operators is more challenging, however, because they contain QCD
processes.

This approach leads to an effective Hamiltonian, with Wilson coefficients which are entirely
independent of the underlying physical processes and can be calculated to a good degree of accuracy
in a range of physics models.
In this way, measurements from different decays all have access to multiple processes, and can be
compared.
Resulting measurements can then be used for predictions of processes, enabling experiments to
favour or disfavour entire classes of NP.



