\section{Summary}

So far, this chapter has motivated the search for NP, and mentioned some of the problems it must
address.
Some references to analyses covered in this thesis have also been made.
The following paragraphs will summarize each analysis and motivate it briefly.

%The decay \btodsphi proceeds via the tree-level annihilation of the constituent quarks of the \Bp
%meson into a \Wp meson.
%This then decays into a $c\bar s$ pair, and an \ssbar is \emph{popped} from the vacuum.
%In the \sm, the decay contains the two CKM matrix elements \V{cs} (which is approximately unity) and
%\V{ub}, which is a source of some contention from the decay $\decay{\Bp}{\taup\nu_\tau}$, which
%is also an annihilation diagram.
%The branching fraction $\BF(\btodsphi)$ is sensitive to NP, because any charged boson can mediate
%the decay, such as a Supersymmetric charged Higgs.
%Furthermore, in the \sm there should be no \CP asymmetry observed, however additional diagrams could
%interfere and cause a significant deviation from zero.
%A study of this decay, in which its branching fraction and \CP-asymmetry are measured, is given in
%\Chap{ch:dsphi}.



%Finally, \Chap{ch:db} describes the direct search for a dark boson, \decay{\db}{\mumu} in the
%decay \decay{\Bd}{\Kstarent\mumu}.
%The dark boson could be a scalar or vector, and could be consistent with a plethora of \bsm
%scenarios.








%\vspace{8pt}
%\begin{flushright}
  %\begin{minipage}{0.95\textwidth}
    \begin{itemize}
  %\setlength{\itemsep}{5pt}
      %\setlength{\itemsep}{8pt}
      \item
        The decay \btodsphi proceeds via the tree-level annihilation of the constituent quarks of the \Bp
        meson into a \Wp boson.
        This then decays into a $c\bar s$ pair, and an \ssbar is created from the QCD field vacuum.
        In the \sm, the decay contains the two CKM matrix elements \V{cs} (which is approximately unity) and
        \V{ub}, which is a source of some contention due to measurements of another
        annihilation-type diagram, namely the decay $\decay{\Bp}{\taup\nu_\tau}$.
        The branching fraction $\BF(\btodsphi)$ is sensitive to NP, because any charged boson can mediate
        the decay, such as a Supersymmetric charged Higgs.
        Furthermore, in the \sm there should be no \CP asymmetry observed, however additional diagrams could
        interfere and cause a significant deviation from zero.
        A study of this decay, in which its branching fraction and \CP-asymmetry are measured, is given in
        \Chap{ch:dsphi}.
      \item
        The \fcnc transition \decay{b}{s\mumu} is forbidden at tree level in the \sm, and instead
        leading order processes are loop diagrams.
        Such transitions are also CKM suppressed in the \sm (by \V{tb} and \V{ts}).
        Just as in the fine tuning of the Higgs mass, virtual \bsm particles can contribute to the decay and
        alter it significantly.
        The decays \btokpipimumu and \btophikmumu are both \decay{b}{s\mumu} \fcnc{s} and could offer
        additional avenues for measuring, for example, $|\V{td}|/|\V{ts}|$.
        There are also an array of strange states that contribute to the \kpipi system, the exact
        spectrum of which is unknown, the same can be said of the \phik spectrum.
        This analysis is outlined in \Chap{ch:hhh}.
      \item
        Finally, \Chap{ch:db} describes the direct search for a dark boson, \decay{\db}{\mumu} in the
        decay \decay{\Bd}{\Kstarent\mumu}.
        The dark boson could be a scalar or vector, and could be consistent with a plethora of \bsm
        scenarios.
    \end{itemize}
  %\end{minipage}
%\end{flushright}








